---
title: '"Hello World"'
author: Mohd Azmi
date: '2021-05-29'
slug: []
categories:
  - R
tags:
  - R
  - RStudio
  - tidyverse
  - ggplot
description: ''
topics: []
---

instead of the common "Hello World" syntax, my first code here will be short R syntax that I'll usually use when I want to show just some simple demo.

of course i'll start with loading tidverse!

```{r}
library(tidyverse)
```

let

1. create some random number using normal distribution syntax rnorm
2. create some random number using uniform distribution syntax runif
3. create new variable with the summation of both number
3. create in data table form with tibble and save in azmi_data

```{r}
azmi_data <- tibble(x = rnorm(50, 5, 2),
               y = runif(50, 0, 10),
               z = x+y)
azmi_data
```

then let plot it with ggplot

1. x and y plot

```{r}
ggplot(azmi_data, aes(x,y)) + geom_point()
```

2. x and z plot

```{r}
ggplot(azmi_data, aes(x,z)) + geom_point()
```

then plot linear regression line to x and z plot

```{r}
ggplot(azmi_data, aes(x,z)) + geom_point() + geom_smooth(method = "lm")
```

so what are the linear regression parameter for the x and z?

```{r}
summary(lm(z ~ x, azmi_data))
```

plot the linear regression using base plot

```{r}
plot(lm(z ~ x, azmi_data))
```




